Sequential rank agreement methods for comparison of ranked lists

### 2015-06-01 latex/paper.Rnw
Added examples

<<fig2a, fig=TRUE,echo=FALSE,include=FALSE,cache=TRUE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig=TRUE>>=
myres <- average_overlap(inputmatrix[,1:2])
myres2 <- average_overlap(inputmatrix[-1,1:2])
xvals <- 1:500
plot(myres, xlim=c(1, 500), type="l")
lines(xvals[-1], myres2, col="red")
@

>>>>

<<fig2a, fig=TRUE,echo=FALSE,include=FALSE,cache=TRUE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
##
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=40))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=20))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig-ao1, echo=FALSE, fig=TRUE,include=FALSE>>=
myres <- average_overlap(inputmatrix[,1:2])
myres2 <- average_overlap(inputmatrix[-c(1,2),1:2])
xvals <- 1:500
plot(myres, xlim=c(1, 300), ylim=c(0,1), type="l")
lines(xvals[-c(1,2)], myres2[1:498], col="red")
@

<<fig-ao2, echo=FALSE, fig=TRUE,include=FALSE>>=
mmyres <- sqrt(sra(inputmatrix[,1:2]))
mmyres2 <- sqrt(sra(inputmatrix[-c(1,2),1:2]))
xvals <- 1:500
plot(mmyres, xlim=c(1, 300), ylim=c(0,1), type="l")
lines(xvals[-c(1,2)], mmyres2[1:498], col="red")
@

\begin{figure}[tb]
\begin{center}
\includegraphics[width=.45\textwidth]{paper-fig-ao1}
\includegraphics[width=.45\textwidth]{paper-fig-ao2}
\end{center}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
 \label{fig:case1}
\end{figure}
